---
title: "A2Sf Visitor Survey Analysis"
author: "Vicky Wang"
output: html_document
---
```{r, echo=FALSE, warning= FALSE, message= FALSE}
library(dplyr)
library(zipcodeR)
library(usdata)
library(knitr)
library(ggplot2)
library(leaflet)
library(sf)
library(tidygeocoder)

```
# Understanding Ann Arbor Summer Festival Visitors, Post-, In- and Combined- Survey Results
```{r, echo=FALSE, warning= FALSE, message= FALSE}
in_season <- readxl::read_xlsx("In Season A2SF Survey data.xlsx")
post_season <- readxl::read_xlsx("Post Season A2SF Survey data.xlsx")
```
## Post-Season Survey Data
*The A2SF post-season survey was disseminated via Instagram, email, _________________(?). This led to bot responses, despite CAPTCHA use. The following code attempts to identify and filter those responses out prior to completing more in-depth analysis, but those data can be easily re-incorporated as needed.*

1. Remove non-US auto-collected countries and manual zip code entries that are not 5 characters
```{r, echo=FALSE, warning= FALSE, message= FALSE}
post_season_clean <- post_season %>%
  filter(nchar(`What is your zip code?`) == 5) %>%
  filter(`Country Code` == "US") 
# initial clean limits zip code entries to 5 digits and countries to the US. non-US entries double-checked via free response quality and readability
```


```{r, echo=FALSE, warning= FALSE, message= FALSE}
post_season_clean$`What is your zip code?` <- as.character(post_season_clean$`What is your zip code?`)
# turns zip code column into character to be analyzed using zipR

is_bot <- function(zip, state) {
  # Handle potential NAs or invalid ZIPs
  if (is.na(zip) || nchar(zip) != 5 || !grepl("^[0-9]+$", zip)) {
    return(TRUE)  # If ZIP code is NA, not 5 characters, or not numeric
  }
  
  # Get state info from ZIP code
  zip_info <- zipcodeR::reverse_zipcode(zip)
  
  # Handle if the lookup fails
  if (is.null(zip_info) || nrow(zip_info) == 0) {
    return(TRUE)  # If ZIP code info is not found
  }
  state <- state2abbr(toupper(state))
  # Check if the provided state matches the ZIP code state
  zip_state <- zip_info$state
  return(zip_state != state)
}
#function to handle abnormal zip-state matchups, marking those not equal as FALSE

```

2. Create a new column that determines initial Bot/Not Bot status by comparing auto-collected Country with manual-collected Zip Code
```{r, echo=FALSE, warning= FALSE, message= FALSE}
elim_bots <- post_season_clean %>%
  mutate(Bot = case_when(
    mapply(is_bot, `What is your zip code?`, State) ~ "Bot",
    TRUE ~ "Not Bot"
  )) %>%
  filter(Bot == "Not Bot")
# created new column that checks whether the zip code inputted and state auto-collected match and labeled seeming Bots accordingly. then filtered on "Not Bots"

elim_bots %>%
  select(`Respondent ID`, State, `Country Code`, Bot) %>%
  head() %>%
  kable()

elim_bots <- elim_bots %>%
  mutate(`Start Date` = as.POSIXct(`Start Date`, format = "%Y-%m-%d %H:%M:%S")) %>%
  mutate(EndDate = as.POSIXct(EndDate, format = "%Y-%m-%d %H:%M:%S")) %>%
  mutate(duration = difftime(EndDate, `Start Date`, units = "secs"))
# no duration is egregiously short to suggest bot presence
```
3. Checked for unusually short-duration surveys based on Start and End Date data. 0 Identified.
```{r, echo=FALSE, warning= FALSE, message= FALSE}
boxplot(elim_bots$duration)

```

4. Created a new file after manually reading responses. Flagged previous "Not Bot"s as "Maybe". Also filtered to leave only "Not Bot" remaining.

```{r, echo=FALSE, warning= FALSE, message= FALSE}
maybe_bots <- read.csv("manually_maybed.csv")
# manually viewed xcel responses to change "Not Bot" to "Maybe" (bot)
```

```{r, echo=FALSE, warning= FALSE, message= FALSE}
hopefully_notbot <- maybe_bots %>%
  filter(Bot == "Not Bot") # removed maybe bots for analysis
```


## **Where are People From?**
```{r, echo=FALSE, warning= FALSE, message= FALSE}
hopefully_notbot$zip_char <- as.character(hopefully_notbot$What.is.your.zip.code.)

zip_codes <- hopefully_notbot %>%
  group_by(zip_char) %>%
  summarise(count = n()) %>%
  mutate(zip_group = case_when(
    zip_char == "48103" ~ "48103",
    zip_char == "48104" ~ "48104",
    zip_char == "48105" ~ "48105",
    zip_char == "48108" ~ "48108",
    zip_char == "48130" ~ "48130",
    zip_char == "48176" ~ "48176",
    zip_char == "48197" ~ "48197",
    zip_char == "48198" ~ "48198",
    zip_char == "48221" ~ "48221",
    TRUE ~ "Other"
  )) %>%
  group_by(zip_group) %>%
  summarise(count = sum(count)) %>%
  ungroup()
```
I collapsed all zip code counts of 1 into a single "Other" categorization.

```{r, echo=FALSE, warning= FALSE, message= FALSE}
zip_codes <- zip_codes %>%
  mutate(
    fraction = count / sum(count),
    ymax = cumsum(fraction),
    ymin = c(0, head(ymax, n = -1)),
    labelPosition = (ymax + ymin) / 2
    )

# Plot
ggplot(zip_codes, aes(ymax = ymax, ymin = ymin, xmax = 4, xmin = 3, fill = zip_group)) +
  geom_rect(color="black") +
  geom_text(x = 4.2, aes(y = labelPosition, label = zip_group), size = 2) + # Position labels outside
  geom_segment(aes(x = 4, xend = 4, y = labelPosition, yend = labelPosition), color = "black") + # Add line from pie to label
  coord_polar(theta = "y") +
  ggtitle("A2SF Visitors by Zip Code") +
  scale_fill_brewer(palette = "PuRd") +
  theme_void() +
  theme(legend.position = "none")
```

```{r, echo=FALSE, warning= FALSE, message= FALSE}
geo_zip <- hopefully_notbot %>%
  group_by(zip_char) %>%
  summarise(count = n()) %>%
  mutate(country = rep("USA", 26))
```

```{r, echo=FALSE, warning= FALSE, message= FALSE}
fix_latlon <- read.csv("geocoded_data.csv")
```
I had to manually geocode some components of latitude and longitude based on zip code because the geocode() function is not perfect. This allows me to map the zip code regions.

## Mapping Where A2SF Visitors are from
* Note that I found 2 additional zip codes that are invalid according to [Free Map Tools](https://www.freemaptools.com/convert-us-zip-code-to-lat-lng.htm).

```{r, echo=FALSE, warning= FALSE, message= FALSE}
leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  setView(lng = -83.7430, lat = 42.2808, zoom = 8) %>%
  addCircleMarkers(
    data = fix_latlon,
    lat = ~latitude,
    lng = ~longitude,
    radius = ~sqrt(count) * 2,  # Adjust the radius based on count
    color = "blue",
    fillColor = "blue",
    fillOpacity = 0.5,
    popup = ~paste("Zip Code:", zip_char, "<br/>", "Count:", count)
  )

```



## Processing ALL ENTRIES TOGETHER
```{r, echo=FALSE, warning= FALSE, message= FALSE}
in_season <- in_season %>%
  mutate(source = "In Season")

post_season <- post_season %>%
  mutate(source = "Post Season")

raw_all_data <- bind_rows(in_season, post_season)
```

```{r, echo=FALSE, warning= FALSE, message= FALSE}
first_clean_all <- raw_all_data %>%
  select(`Respondent ID`,
         source,
         everything()
         )
```

```{r, echo=FALSE, warning= FALSE, message= FALSE}
combined <- read.csv("combined_all_raw.csv")
```

```{r, echo=FALSE, warning= FALSE, message= FALSE}
combined <- combined %>%
  rename(ID = Respondent.ID,
         survey = source,
         start_date = Start.Date,
         end_date = EndDate,
         country_code = Country.Code,
         country = Country.Name,
         state = State,
         zip_code = What.is.your.zip.code.,
         age = What.is.your.age.,
         gender = With.what.gender.do.you.most.identify.,
         other_gender_identity = Gender.Identity.Other,
         edu = What.is.your.education.level.,
         race_ethnicity = Which.of.the.following.describes.your.race.and.or.ethnicity..Note..we.recognize.the.following.list.is.not.all.encompassing.for.how.people.may.identify..Please.select.all.that.apply..and.in.addition..you.may.further.self.describe.race.and.or.ethnicity.using.the..Other..option...,
         other_race_ethnicity = Race_Ethnicity.Other,
         household_income = What.was.your.gross.household.income.during.the.last.year.,
         attendance = How.many.times.each.year.do.you.typically.attend.Top.of.the.Park.,
         attendance_factors_tn = What.were.the.biggest.factors.that.influenced.your.decision.whether.or.not.to.attend..Select.all.that.apply.,
         other_favorite_offerings_tn = Favorite.Offerings.Other,
         spend = On.average..how.much.money.do.you.spend.at.Top.of.the.Park.each.year..drinks..food..merchandise..etc...,
         donation = A2SF.is.an.independent..community.supported.501.c.3.nonprofit.organization..with.individual.donors.contributing..340.000.or.20..of.our.yearly.budget..How.likely.are.you.to.donate.to.our.organization.,
         future_attendance_likelihood = On.a.scale.of.1.10..how.likely.are.you.to.attend.one.of.our.events.in.the.future.,
         recommend_likelihood = On.a.scale.of.1.10..how.likely.are.you.to.recommend.our.events.to.a.friend.or.family.member.,
         family_offerings_satisfaction = On.a.scale.of.1.10..how.satisfied.are.you.with.family.offerings..KidZone..Kids.Rock..at.Top.of.the.Park., 
         music_satisfaction = On.a.scale.of.1.10..how.satisfied.are.you.with.the.Top.of.the.Park.music.programming.,
         overall_trajectory = On.a.scale.of.1.10..how.do.you.feel.about.the.overall.trajectory.that.A2SF.is.heading.in.,
         anything_else = Is.there.anything.else.you.would.like.to.share.about.Top.of.the.Park.or.A2SF.as.an.organization.,
         accessibility = What.would.make.it.easier.for.you.to.participate.in.A2SF.events.,
         how_did_you_hear = How.did.you.hear.about.A2SF.at.Top.of.the.Park.,
         email = If.you.would.like.to.be.entered.to.win.a..50.gift.card..please.provide.your.email.address.,
         mailing_list = If.you.provided.your.email..do.you.want.to.be.added.to.our.mailing.list.,
         attendance_post = How.many.times.DID.you.attend.Top.of.the.Park.this.season.,
         offerings_post = What.WERE.your.favorite.offerings.this.season...Choose.up.to.three.,
         spent = On.average..how.much.money.DID.you.spend.at.Top.of.the.Park.this.season..drinks..food..merchandise..etc...,
         all_attendance = Times.Attended..IGNORE.SOURCE.,
         all_fav_offerings = Favorite.Offerings..IGNORE.SOURCE.,
         all_money_spent = Money.Spent..IGNORE.SOURCE.)
```

```{r, echo=FALSE, warning= FALSE, message= FALSE}
combined <- combined %>%
  rename(other_attendance_factors = Attendance.Other,
         favorite_offerings_tn = What.are.your.favorite.offerings.tonight...Choose.up.to.three.)
```


```{r, echo=FALSE, warning= FALSE, message= FALSE}
zc_metadata_df <- reverse_zipcode(combined$zip_code)

remove_incorrect_state_zip <- combined %>%
  left_join(zc_metadata_df, by = c("zip_code" = "zipcode")) %>%
  mutate(state_abbreviation = state2abbr(state.x)) %>%
  filter(state.y == state_abbreviation | country_code != "US")
```